
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
getwd()
setwd("/Users/divyadesadla/Desktop/CMU/CMUFall19/Data Science for Biological Sciences/Homework3")
Puncta <- read.csv("PVandPOM.csv",header=TRUE)
head(Puncta)
```

```{r}
LogPuncta <- cbind(Puncta[,1:2],log(Puncta[,3:14]+1e-6),Puncta[,15:16])
```

```{r}
write.table(LogPuncta,"LogPuncta.txt")
```

```{r}
LogPuncta <- read.table("LogPuncta.txt")
```

```{r}
TrainingRows <- (n=runif(dim(LogPuncta)[1])>0.1)
TestingRows <- !TrainingRows
TrainingInputs <- do.call(cbind, subset(LogPuncta[,3:14],TrainingRows))
TrainingOutputs <- subset(LogPuncta[,"Presynaptic.association"]=="PV",TrainingRows)
TrainData <- cbind(TrainingInputs,TrainingOutputs)
colnames(TrainData)[13] <- "Output"

TestingInputs <- do.call(cbind, subset(LogPuncta[,3:14],TestingRows))
TestingOutputs <- subset(LogPuncta[,"Presynaptic.association"]=="PV",TestingRows)
TestingData <- cbind(TestingInputs,TestingOutputs)
colnames(TestingData)[13] <- "Output"
```

```{r}
CVLogisticFit <- glm(formula= Output ~ Area + Ellipticity..oblate.
                     + Intensity.Median,
                     data=as.data.frame(TrainData),
                     family=binomial(link='logit'))
CVLogisticFit
CVLogisticFit$coefficients
```


```{r}
TrainTP <- sum(TrainingOutputs & (CVLogisticFit$fitted.values>0.5))
TrainTN <- sum(!TrainingOutputs & !(CVLogisticFit$fitted.values>0.5))
TrainFP <- sum(!TrainingOutputs & (CVLogisticFit$fitted.values>0.5))
TrainFN <- sum(TrainingOutputs & !(CVLogisticFit$fitted.values>0.5))


Accuracy <- (TrainTP+TrainTN)/(TrainTP+TrainTN+TrainFP+ TrainFN)
Sensitivity <- (TrainTP)/(TrainTP+TrainFN)
Specificity<- (TrainTN)/(TrainTN+ TrainFP)
Precision<- (TrainTP)/(TrainTP+ TrainFP)
F_score <- (2*TrainTP)/(2* TrainTP+ TrainFP+ TrainFN)
```

```{r}
CVLogisticFit <- glm(formula= Output ~ Area + Ellipticity..oblate. + Ellipticity..prolate. + Intensity.Max + Intensity.Mean
                     + Intensity.Median + Intensity.Min + Intensity.StdDev + Intensity.Sum + Number.of.Vertices + Sphericity
                     + Volume, 
                     data=as.data.frame(TrainData),
                     family=binomial(link='logit'))
CVLogisticFit
CVLogisticFit$coefficients
```

```{r}
TrainTP <- sum(TrainingOutputs & (CVLogisticFit$fitted.values>0.5))
TrainTN <- sum(!TrainingOutputs & !(CVLogisticFit$fitted.values>0.5))
TrainFP <- sum(!TrainingOutputs & (CVLogisticFit$fitted.values>0.5))
TrainFN <- sum(TrainingOutputs & !(CVLogisticFit$fitted.values>0.5))

Accuracy <- (TrainTP+TrainTN)/(TrainTP+TrainTN+TrainFP+ TrainFN)
Accuracy

```

```{r}
CVPredictions <- predict(CVLogisticFit,as.data.frame(cbind(TestingInputs,TestingOutputs)),type="response")
```

```{r}
TestTP <- sum(TestingOutputs & (CVPredictions>0.5))
TestTN <- sum(!TestingOutputs & !( CVPredictions >0.5))
TestFP <- sum(!TestingOutputs & (CVPredictions >0.5))
TestFN <- sum(TestingOutputs & !( CVPredictions >0.5))

Accuracy <- (TestTP+TestTN)/(TestTP+TestTN+TestFP+ TestFN)
Accuracy
```

```{r}
chisq.test(matrix(data=c(TestTP,TestFP,TestFN,TestTN),nrow=2,ncol=2))
```

```{r}
CVLogisticFit <- glm(formula= Output ~ Area + Ellipticity..oblate. + 
                   Intensity.Median +  Volume, 
                   data=as.data.frame(TrainData), 
                   family=binomial(link='logit'))
CVLogisticFit$coefficients
```

```{r}
TrainTP <- sum(TrainingOutputs & (CVLogisticFit$fitted.values>0.5))
TrainTN <- sum(!TrainingOutputs & !(CVLogisticFit$fitted.values>0.5))
TrainFP <- sum(!TrainingOutputs & (CVLogisticFit$fitted.values>0.5))
TrainFN <- sum(TrainingOutputs & !(CVLogisticFit$fitted.values>0.5))

Accuracy <- (TrainTP+TrainTN)/(TrainTP+TrainTN+TrainFP+ TrainFN)
Accuracy

```

CVLogisticFit <- glm(formula= Output ~ Area + Ellipticity..oblate. + 
                   Intensity.Median,
                   data=as.data.frame(TrainData), 
                   family=binomial(link='logit'))
CVLogisticFit$coefficients
```
```{r}
TrainTP <- sum(TrainingOutputs & (CVLogisticFit$fitted.values>0.5))
TrainTN <- sum(!TrainingOutputs & !(CVLogisticFit$fitted.values>0.5))
TrainFP <- sum(!TrainingOutputs & (CVLogisticFit$fitted.values>0.5))
TrainFN <- sum(TrainingOutputs & !(CVLogisticFit$fitted.values>0.5))

Accuracy <- (TrainTP+TrainTN)/(TrainTP+TrainTN+TrainFP+ TrainFN)
Accuracy
```

```{r}
CVPredictions <- predict(CVLogisticFit,as.data.frame(cbind(TestingInputs,TestingOutputs)),type="response")
```

```{r}
TestTP <- sum(TestingOutputs & (CVPredictions>0.5))
TestTN <- sum(!TestingOutputs & !( CVPredictions >0.5))
TestFP <- sum(!TestingOutputs & (CVPredictions >0.5))
TestFN <- sum(TestingOutputs & !( CVPredictions >0.5))

Accuracy <- (TestTP+TestTN)/(TestTP+TestTN+TestFP+ TestFN)
Accuracy
```
```{r}
chisq.test(matrix(data=c(TestTP,TestFP,TestFN,TestTN),nrow=2,ncol=2))
```

```{r}
CVLogisticFit <- glm(formula= Output ~ Area + Ellipticity..oblate. + 
                   Intensity.Median +  Intensity.Max, 
                   data=as.data.frame(TrainData), 
                   family=binomial(link='logit'))
CVLogisticFit$coefficients
```
```{r}
TrainTP <- sum(TrainingOutputs & (CVLogisticFit$fitted.values>0.5))
TrainTN <- sum(!TrainingOutputs & !(CVLogisticFit$fitted.values>0.5))
TrainFP <- sum(!TrainingOutputs & (CVLogisticFit$fitted.values>0.5))
TrainFN <- sum(TrainingOutputs & !(CVLogisticFit$fitted.values>0.5))

Accuracy <- (TrainTP+TrainTN)/(TrainTP+TrainTN+TrainFP+ TrainFN)
Accuracy
```

```{r}
CVPredictions <- predict(CVLogisticFit,as.data.frame(cbind(TestingInputs,TestingOutputs)),type="response")
```

```{r}
TestTP <- sum(TestingOutputs & (CVPredictions>0.5))
TestTN <- sum(!TestingOutputs & !( CVPredictions >0.5))
TestFP <- sum(!TestingOutputs & (CVPredictions >0.5))
TestFN <- sum(TestingOutputs & !( CVPredictions >0.5))

Accuracy <- (TestTP+TestTN)/(TestTP+TestTN+TestFP+ TestFN)
Accuracy
```
```{r}
chisq.test(matrix(data=c(TestTP,TestFP,TestFN,TestTN),nrow=2,ncol=2))
```

```{r}
CVLogisticFit <- glm(formula= Output ~ Area + Ellipticity..oblate. + 
                   Intensity.Median +  Intensity.Min, 
                   data=as.data.frame(TrainData), 
                   family=binomial(link='logit'))
CVLogisticFit$coefficients
```
```{r}
TrainTP <- sum(TrainingOutputs & (CVLogisticFit$fitted.values>0.5))
TrainTN <- sum(!TrainingOutputs & !(CVLogisticFit$fitted.values>0.5))
TrainFP <- sum(!TrainingOutputs & (CVLogisticFit$fitted.values>0.5))
TrainFN <- sum(TrainingOutputs & !(CVLogisticFit$fitted.values>0.5))

Accuracy <- (TrainTP+TrainTN)/(TrainTP+TrainTN+TrainFP+ TrainFN)
Accuracy
```

```{r}
CVPredictions <- predict(CVLogisticFit,as.data.frame(cbind(TestingInputs,TestingOutputs)),type="response")
```

```{r}
TestTP <- sum(TestingOutputs & (CVPredictions>0.5))
TestTN <- sum(!TestingOutputs & !( CVPredictions >0.5))
TestFP <- sum(!TestingOutputs & (CVPredictions >0.5))
TestFN <- sum(TestingOutputs & !( CVPredictions >0.5))

Accuracy <- (TestTP+TestTN)/(TestTP+TestTN+TestFP+ TestFN)
Accuracy
```
```{r}
chisq.test(matrix(data=c(TestTP,TestFP,TestFN,TestTN),nrow=2,ncol=2))
```


```{r}
CVLogisticFit <- glm(formula= Output ~ Area + Ellipticity..oblate. + 
                   Intensity.Median +  Intensity.Mean, 
                   data=as.data.frame(TrainData), 
                   family=binomial(link='logit'))
CVLogisticFit$coefficients
```
```{r}
TrainTP <- sum(TrainingOutputs & (CVLogisticFit$fitted.values>0.5))
TrainTN <- sum(!TrainingOutputs & !(CVLogisticFit$fitted.values>0.5))
TrainFP <- sum(!TrainingOutputs & (CVLogisticFit$fitted.values>0.5))
TrainFN <- sum(TrainingOutputs & !(CVLogisticFit$fitted.values>0.5))

Accuracy <- (TrainTP+TrainTN)/(TrainTP+TrainTN+TrainFP+ TrainFN)
Accuracy
```

```{r}
CVPredictions <- predict(CVLogisticFit,as.data.frame(cbind(TestingInputs,TestingOutputs)),type="response")
```

```{r}
TestTP <- sum(TestingOutputs & (CVPredictions>0.5))
TestTN <- sum(!TestingOutputs & !( CVPredictions >0.5))
TestFP <- sum(!TestingOutputs & (CVPredictions >0.5))
TestFN <- sum(TestingOutputs & !( CVPredictions >0.5))

Accuracy <- (TestTP+TestTN)/(TestTP+TestTN+TestFP+ TestFN)
Accuracy
```
```{r}
chisq.test(matrix(data=c(TestTP,TestFP,TestFN,TestTN),nrow=2,ncol=2))
```

```{r}
CVLogisticFit <- glm(formula= Output ~ Area + Ellipticity..oblate. + 
                   Intensity.Median +  Intensity.StdDev, 
                   data=as.data.frame(TrainData), 
                   family=binomial(link='logit'))
CVLogisticFit$coefficients
```
```{r}
TrainTP <- sum(TrainingOutputs & (CVLogisticFit$fitted.values>0.5))
TrainTN <- sum(!TrainingOutputs & !(CVLogisticFit$fitted.values>0.5))
TrainFP <- sum(!TrainingOutputs & (CVLogisticFit$fitted.values>0.5))
TrainFN <- sum(TrainingOutputs & !(CVLogisticFit$fitted.values>0.5))

Accuracy <- (TrainTP+TrainTN)/(TrainTP+TrainTN+TrainFP+ TrainFN)
Accuracy
```

```{r}
CVPredictions <- predict(CVLogisticFit,as.data.frame(cbind(TestingInputs,TestingOutputs)),type="response")
```

```{r}
TestTP <- sum(TestingOutputs & (CVPredictions>0.5))
TestTN <- sum(!TestingOutputs & !( CVPredictions >0.5))
TestFP <- sum(!TestingOutputs & (CVPredictions >0.5))
TestFN <- sum(TestingOutputs & !( CVPredictions >0.5))

Accuracy <- (TestTP+TestTN)/(TestTP+TestTN+TestFP+ TestFN)
Accuracy
```
```{r}
chisq.test(matrix(data=c(TestTP,TestFP,TestFN,TestTN),nrow=2,ncol=2))
```

```{r}
CVLogisticFit <- glm(formula= Output ~ Area + Ellipticity..oblate. + 
                   Intensity.Median +  Intensity.Sum, 
                   data=as.data.frame(TrainData), 
                   family=binomial(link='logit'))
CVLogisticFit$coefficients
```
```{r}
TrainTP <- sum(TrainingOutputs & (CVLogisticFit$fitted.values>0.5))
TrainTN <- sum(!TrainingOutputs & !(CVLogisticFit$fitted.values>0.5))
TrainFP <- sum(!TrainingOutputs & (CVLogisticFit$fitted.values>0.5))
TrainFN <- sum(TrainingOutputs & !(CVLogisticFit$fitted.values>0.5))

Accuracy <- (TrainTP+TrainTN)/(TrainTP+TrainTN+TrainFP+ TrainFN)
Accuracy
```

```{r}
CVPredictions <- predict(CVLogisticFit,as.data.frame(cbind(TestingInputs,TestingOutputs)),type="response")
```

```{r}
TestTP <- sum(TestingOutputs & (CVPredictions>0.5))
TestTN <- sum(!TestingOutputs & !( CVPredictions >0.5))
TestFP <- sum(!TestingOutputs & (CVPredictions >0.5))
TestFN <- sum(TestingOutputs & !( CVPredictions >0.5))

Accuracy <- (TestTP+TestTN)/(TestTP+TestTN+TestFP+ TestFN)
Accuracy
```
```{r}
chisq.test(matrix(data=c(TestTP,TestFP,TestFN,TestTN),nrow=2,ncol=2))
```

```{r}
CVLogisticFit <- glm(formula= Output ~ Area + Ellipticity..oblate. + 
                   Intensity.Median +  Number.of.Vertices, 
                   data=as.data.frame(TrainData), 
                   family=binomial(link='logit'))
CVLogisticFit$coefficients
```
```{r}
TrainTP <- sum(TrainingOutputs & (CVLogisticFit$fitted.values>0.5))
TrainTN <- sum(!TrainingOutputs & !(CVLogisticFit$fitted.values>0.5))
TrainFP <- sum(!TrainingOutputs & (CVLogisticFit$fitted.values>0.5))
TrainFN <- sum(TrainingOutputs & !(CVLogisticFit$fitted.values>0.5))

Accuracy <- (TrainTP+TrainTN)/(TrainTP+TrainTN+TrainFP+ TrainFN)
Accuracy
```

```{r}
CVPredictions <- predict(CVLogisticFit,as.data.frame(cbind(TestingInputs,TestingOutputs)),type="response")
```

```{r}
TestTP <- sum(TestingOutputs & (CVPredictions>0.5))
TestTN <- sum(!TestingOutputs & !( CVPredictions >0.5))
TestFP <- sum(!TestingOutputs & (CVPredictions >0.5))
TestFN <- sum(TestingOutputs & !( CVPredictions >0.5))

Accuracy <- (TestTP+TestTN)/(TestTP+TestTN+TestFP+ TestFN)
Accuracy
```
```{r}
chisq.test(matrix(data=c(TestTP,TestFP,TestFN,TestTN),nrow=2,ncol=2))
```

```{r}
CVLogisticFit <- glm(formula= Output ~ Area + Ellipticity..oblate. + 
                   Intensity.Median +  Sphericity, 
                   data=as.data.frame(TrainData), 
                   family=binomial(link='logit'))
CVLogisticFit$coefficients
```
```{r}
TrainTP <- sum(TrainingOutputs & (CVLogisticFit$fitted.values>0.5))
TrainTN <- sum(!TrainingOutputs & !(CVLogisticFit$fitted.values>0.5))
TrainFP <- sum(!TrainingOutputs & (CVLogisticFit$fitted.values>0.5))
TrainFN <- sum(TrainingOutputs & !(CVLogisticFit$fitted.values>0.5))

Accuracy <- (TrainTP+TrainTN)/(TrainTP+TrainTN+TrainFP+ TrainFN)
Accuracy
```

```{r}
CVPredictions <- predict(CVLogisticFit,as.data.frame(cbind(TestingInputs,TestingOutputs)),type="response")
```

```{r}
TestTP <- sum(TestingOutputs & (CVPredictions>0.5))
TestTN <- sum(!TestingOutputs & !( CVPredictions >0.5))
TestFP <- sum(!TestingOutputs & (CVPredictions >0.5))
TestFN <- sum(TestingOutputs & !( CVPredictions >0.5))

Accuracy <- (TestTP+TestTN)/(TestTP+TestTN+TestFP+ TestFN)
Accuracy
```
```{r}
chisq.test(matrix(data=c(TestTP,TestFP,TestFN,TestTN),nrow=2,ncol=2))
```

```{r}
CVLogisticFit <- glm(formula= Output ~ Area + Ellipticity..oblate. + 
                   Intensity.Median + Intensity.Max,
                   data=as.data.frame(TrainData), 
                   family=binomial(link='logit'))
CVLogisticFit$coefficients
```
```{r}
TrainTP <- sum(TrainingOutputs & (CVLogisticFit$fitted.values>0.5))
TrainTN <- sum(!TrainingOutputs & !(CVLogisticFit$fitted.values>0.5))
TrainFP <- sum(!TrainingOutputs & (CVLogisticFit$fitted.values>0.5))
TrainFN <- sum(TrainingOutputs & !(CVLogisticFit$fitted.values>0.5))

Accuracy <- (TrainTP+TrainTN)/(TrainTP+TrainTN+TrainFP+ TrainFN)
Accuracy
```

```{r}
CVPredictions <- predict(CVLogisticFit,as.data.frame(cbind(TestingInputs,TestingOutputs)),type="response")
```

```{r}
TestTP <- sum(TestingOutputs & (CVPredictions>0.5))
TestTN <- sum(!TestingOutputs & !( CVPredictions >0.5))
TestFP <- sum(!TestingOutputs & (CVPredictions >0.5))
TestFN <- sum(TestingOutputs & !( CVPredictions >0.5))

Accuracy <- (TestTP+TestTN)/(TestTP+TestTN+TestFP+ TestFN)
Accuracy
```
```{r}
chisq.test(matrix(data=c(TestTP,TestFP,TestFN,TestTN),nrow=2,ncol=2))
```

```{r}
CVLogisticFit <- glm(formula= Output ~ Area + Ellipticity..oblate. + 
                   Intensity.Median + Intensity.Max + Intensity.Min, 
                   data=as.data.frame(TrainData), 
                   family=binomial(link='logit'))
CVLogisticFit$coefficients
```
```{r}
TrainTP <- sum(TrainingOutputs & (CVLogisticFit$fitted.values>0.5))
TrainTN <- sum(!TrainingOutputs & !(CVLogisticFit$fitted.values>0.5))
TrainFP <- sum(!TrainingOutputs & (CVLogisticFit$fitted.values>0.5))
TrainFN <- sum(TrainingOutputs & !(CVLogisticFit$fitted.values>0.5))

Accuracy <- (TrainTP+TrainTN)/(TrainTP+TrainTN+TrainFP+ TrainFN)
Accuracy
```

```{r}
CVPredictions <- predict(CVLogisticFit,as.data.frame(cbind(TestingInputs,TestingOutputs)),type="response")
```

```{r}
TestTP <- sum(TestingOutputs & (CVPredictions>0.5))
TestTN <- sum(!TestingOutputs & !( CVPredictions >0.5))
TestFP <- sum(!TestingOutputs & (CVPredictions >0.5))
TestFN <- sum(TestingOutputs & !( CVPredictions >0.5))

Accuracy <- (TestTP+TestTN)/(TestTP+TestTN+TestFP+ TestFN)
Accuracy
```
```{r}
chisq.test(matrix(data=c(TestTP,TestFP,TestFN,TestTN),nrow=2,ncol=2))
```

```{r}
CVLogisticFit <- glm(formula= Output ~ Area + Ellipticity..oblate. + 
                   Intensity.Median + Intensity.Max +  Intensity.Mean, 
                   data=as.data.frame(TrainData), 
                   family=binomial(link='logit'))
CVLogisticFit$coefficients
```
```{r}
TrainTP <- sum(TrainingOutputs & (CVLogisticFit$fitted.values>0.5))
TrainTN <- sum(!TrainingOutputs & !(CVLogisticFit$fitted.values>0.5))
TrainFP <- sum(!TrainingOutputs & (CVLogisticFit$fitted.values>0.5))
TrainFN <- sum(TrainingOutputs & !(CVLogisticFit$fitted.values>0.5))

Accuracy <- (TrainTP+TrainTN)/(TrainTP+TrainTN+TrainFP+ TrainFN)
Accuracy
```

```{r}
CVPredictions <- predict(CVLogisticFit,as.data.frame(cbind(TestingInputs,TestingOutputs)),type="response")
```

```{r}
TestTP <- sum(TestingOutputs & (CVPredictions>0.5))
TestTN <- sum(!TestingOutputs & !( CVPredictions >0.5))
TestFP <- sum(!TestingOutputs & (CVPredictions >0.5))
TestFN <- sum(TestingOutputs & !( CVPredictions >0.5))

Accuracy <- (TestTP+TestTN)/(TestTP+TestTN+TestFP+ TestFN)
Accuracy
```
```{r}
chisq.test(matrix(data=c(TestTP,TestFP,TestFN,TestTN),nrow=2,ncol=2))
```

```{r}
CVLogisticFit <- glm(formula= Output ~ Area + Ellipticity..oblate. + 
                   Intensity.Median + Intensity.Max + Intensity.StdDev, 
                   data=as.data.frame(TrainData), 
                   family=binomial(link='logit'))
CVLogisticFit$coefficients
```
```{r}
TrainTP <- sum(TrainingOutputs & (CVLogisticFit$fitted.values>0.5))
TrainTN <- sum(!TrainingOutputs & !(CVLogisticFit$fitted.values>0.5))
TrainFP <- sum(!TrainingOutputs & (CVLogisticFit$fitted.values>0.5))
TrainFN <- sum(TrainingOutputs & !(CVLogisticFit$fitted.values>0.5))

Accuracy <- (TrainTP+TrainTN)/(TrainTP+TrainTN+TrainFP+ TrainFN)
Accuracy
```

```{r}
CVPredictions <- predict(CVLogisticFit,as.data.frame(cbind(TestingInputs,TestingOutputs)),type="response")
```

```{r}
TestTP <- sum(TestingOutputs & (CVPredictions>0.5))
TestTN <- sum(!TestingOutputs & !( CVPredictions >0.5))
TestFP <- sum(!TestingOutputs & (CVPredictions >0.5))
TestFN <- sum(TestingOutputs & !( CVPredictions >0.5))

Accuracy <- (TestTP+TestTN)/(TestTP+TestTN+TestFP+ TestFN)
Accuracy
```
```{r}
chisq.test(matrix(data=c(TestTP,TestFP,TestFN,TestTN),nrow=2,ncol=2))
```

```{r}
CVLogisticFit <- glm(formula= Output ~ Area + Ellipticity..oblate. + 
                   Intensity.Median + Intensity.Max + Intensity.Sum, 
                   data=as.data.frame(TrainData), 
                   family=binomial(link='logit'))
CVLogisticFit$coefficients
```
```{r}
TrainTP <- sum(TrainingOutputs & (CVLogisticFit$fitted.values>0.5))
TrainTN <- sum(!TrainingOutputs & !(CVLogisticFit$fitted.values>0.5))
TrainFP <- sum(!TrainingOutputs & (CVLogisticFit$fitted.values>0.5))
TrainFN <- sum(TrainingOutputs & !(CVLogisticFit$fitted.values>0.5))

Accuracy <- (TrainTP+TrainTN)/(TrainTP+TrainTN+TrainFP+ TrainFN)
Accuracy
```

```{r}
CVPredictions <- predict(CVLogisticFit,as.data.frame(cbind(TestingInputs,TestingOutputs)),type="response")
```

```{r}
TestTP <- sum(TestingOutputs & (CVPredictions>0.5))
TestTN <- sum(!TestingOutputs & !( CVPredictions >0.5))
TestFP <- sum(!TestingOutputs & (CVPredictions >0.5))
TestFN <- sum(TestingOutputs & !( CVPredictions >0.5))

Accuracy <- (TestTP+TestTN)/(TestTP+TestTN+TestFP+ TestFN)
Accuracy
```
```{r}
chisq.test(matrix(data=c(TestTP,TestFP,TestFN,TestTN),nrow=2,ncol=2))
```

```{r}
CVLogisticFit <- glm(formula= Output ~ Area + Ellipticity..oblate. + 
                   Intensity.Median + Intensity.Max + Number.of.Vertices, 
                   data=as.data.frame(TrainData), 
                   family=binomial(link='logit'))
CVLogisticFit$coefficients
```
```{r}
TrainTP <- sum(TrainingOutputs & (CVLogisticFit$fitted.values>0.5))
TrainTN <- sum(!TrainingOutputs & !(CVLogisticFit$fitted.values>0.5))
TrainFP <- sum(!TrainingOutputs & (CVLogisticFit$fitted.values>0.5))
TrainFN <- sum(TrainingOutputs & !(CVLogisticFit$fitted.values>0.5))

Accuracy <- (TrainTP+TrainTN)/(TrainTP+TrainTN+TrainFP+ TrainFN)
Accuracy
```

```{r}
CVPredictions <- predict(CVLogisticFit,as.data.frame(cbind(TestingInputs,TestingOutputs)),type="response")
```

```{r}
TestTP <- sum(TestingOutputs & (CVPredictions>0.5))
TestTN <- sum(!TestingOutputs & !( CVPredictions >0.5))
TestFP <- sum(!TestingOutputs & (CVPredictions >0.5))
TestFN <- sum(TestingOutputs & !( CVPredictions >0.5))

Accuracy <- (TestTP+TestTN)/(TestTP+TestTN+TestFP+ TestFN)
Accuracy
```
```{r}
chisq.test(matrix(data=c(TestTP,TestFP,TestFN,TestTN),nrow=2,ncol=2))
```

```{r}
CVLogisticFit <- glm(formula= Output ~ Area + Ellipticity..oblate. + 
                   Intensity.Median + Intensity.Max +  Sphericity, 
                   data=as.data.frame(TrainData), 
                   family=binomial(link='logit'))
CVLogisticFit$coefficients
```
```{r}
TrainTP <- sum(TrainingOutputs & (CVLogisticFit$fitted.values>0.5))
TrainTN <- sum(!TrainingOutputs & !(CVLogisticFit$fitted.values>0.5))
TrainFP <- sum(!TrainingOutputs & (CVLogisticFit$fitted.values>0.5))
TrainFN <- sum(TrainingOutputs & !(CVLogisticFit$fitted.values>0.5))

Accuracy <- (TrainTP+TrainTN)/(TrainTP+TrainTN+TrainFP+ TrainFN)
Accuracy
```

```{r}
CVPredictions <- predict(CVLogisticFit,as.data.frame(cbind(TestingInputs,TestingOutputs)),type="response")
```

```{r}
TestTP <- sum(TestingOutputs & (CVPredictions>0.5))
TestTN <- sum(!TestingOutputs & !( CVPredictions >0.5))
TestFP <- sum(!TestingOutputs & (CVPredictions >0.5))
TestFN <- sum(TestingOutputs & !( CVPredictions >0.5))

Accuracy <- (TestTP+TestTN)/(TestTP+TestTN+TestFP+ TestFN)
Accuracy
```
```{r}
chisq.test(matrix(data=c(TestTP,TestFP,TestFN,TestTN),nrow=2,ncol=2))
```

```{r}
CVLogisticFit <- glm(formula= Output ~ Area + Ellipticity..oblate. + Ellipticity..prolate. + Number.of.Vertices + Sphericity
                     + Volume, 
                   data=as.data.frame(TrainData), 
                   family=binomial(link='logit'))
CVLogisticFit$coefficients
```
```{r}
TrainTP <- sum(TrainingOutputs & (CVLogisticFit$fitted.values>0.5))
TrainTN <- sum(!TrainingOutputs & !(CVLogisticFit$fitted.values>0.5))
TrainFP <- sum(!TrainingOutputs & (CVLogisticFit$fitted.values>0.5))
TrainFN <- sum(TrainingOutputs & !(CVLogisticFit$fitted.values>0.5))

Accuracy <- (TrainTP+TrainTN)/(TrainTP+TrainTN+TrainFP+ TrainFN)
Accuracy
```

```{r}
CVPredictions <- predict(CVLogisticFit,as.data.frame(cbind(TestingInputs,TestingOutputs)),type="response")
```

```{r}
TestTP <- sum(TestingOutputs & (CVPredictions>0.5))
TestTN <- sum(!TestingOutputs & !( CVPredictions >0.5))
TestFP <- sum(!TestingOutputs & (CVPredictions >0.5))
TestFN <- sum(TestingOutputs & !( CVPredictions >0.5))

Accuracy <- (TestTP+TestTN)/(TestTP+TestTN+TestFP+ TestFN)
Accuracy
```
```{r}
chisq.test(matrix(data=c(TestTP,TestFP,TestFN,TestTN),nrow=2,ncol=2))
```

```{r}
CVLogisticFit <- glm(formula= Output ~ Area + Area^2 + Ellipticity..oblate. + Ellipticity..oblate.^2 + Ellipticity..prolate. + Ellipticity..prolate.^2 + Intensity.Max + Intensity.Max^2 + Intensity.Mean + Intensity.Mean^2
                     + Intensity.Median + Intensity.Median^2 + Intensity.Min + Intensity.Min^2 + Intensity.StdDev + Intensity.StdDev^2 + Intensity.Sum + Intensity.Sum^2 + Number.of.Vertices + Number.of.Vertices^2 + Sphericity + Sphericity^2
                     + Volume + Volume^2,  
                   data=as.data.frame(TrainData), 
                   family=binomial(link='logit'))
CVLogisticFit$coefficients
```
```{r}
TrainTP <- sum(TrainingOutputs & (CVLogisticFit$fitted.values>0.5))
TrainTN <- sum(!TrainingOutputs & !(CVLogisticFit$fitted.values>0.5))
TrainFP <- sum(!TrainingOutputs & (CVLogisticFit$fitted.values>0.5))
TrainFN <- sum(TrainingOutputs & !(CVLogisticFit$fitted.values>0.5))

Accuracy <- (TrainTP+TrainTN)/(TrainTP+TrainTN+TrainFP+ TrainFN)
Accuracy
```

```{r}
CVPredictions <- predict(CVLogisticFit,as.data.frame(cbind(TestingInputs,TestingOutputs)),type="response")
```

```{r}
TestTP <- sum(TestingOutputs & (CVPredictions>0.5))
TestTN <- sum(!TestingOutputs & !( CVPredictions >0.5))
TestFP <- sum(!TestingOutputs & (CVPredictions >0.5))
TestFN <- sum(TestingOutputs & !( CVPredictions >0.5))

Accuracy <- (TestTP+TestTN)/(TestTP+TestTN+TestFP+ TestFN)
Accuracy
```
```{r}
chisq.test(matrix(data=c(TestTP,TestFP,TestFN,TestTN),nrow=2,ncol=2))
```

```{r}
CVLogisticFit <- glm(formula= Output ~ Area + Area^2 + Ellipticity..oblate. + Ellipticity..oblate.^2 + Ellipticity..prolate. + Ellipticity..prolate.^2 + Number.of.Vertices + Number.of.Vertices^2 + Sphericity + Sphericity^2
                     + Volume + Volume^2, 
                   data=as.data.frame(TrainData), 
                   family=binomial(link='logit'))
CVLogisticFit$coefficients
```
```{r}
TrainTP <- sum(TrainingOutputs & (CVLogisticFit$fitted.values>0.5))
TrainTN <- sum(!TrainingOutputs & !(CVLogisticFit$fitted.values>0.5))
TrainFP <- sum(!TrainingOutputs & (CVLogisticFit$fitted.values>0.5))
TrainFN <- sum(TrainingOutputs & !(CVLogisticFit$fitted.values>0.5))

Accuracy <- (TrainTP+TrainTN)/(TrainTP+TrainTN+TrainFP+ TrainFN)
Accuracy
```

```{r}
CVPredictions <- predict(CVLogisticFit,as.data.frame(cbind(TestingInputs,TestingOutputs)),type="response")
```

```{r}
TestTP <- sum(TestingOutputs & (CVPredictions>0.5))
TestTN <- sum(!TestingOutputs & !( CVPredictions >0.5))
TestFP <- sum(!TestingOutputs & (CVPredictions >0.5))
TestFN <- sum(TestingOutputs & !( CVPredictions >0.5))

Accuracy <- (TestTP+TestTN)/(TestTP+TestTN+TestFP+ TestFN)
Accuracy
```
```{r}
chisq.test(matrix(data=c(TestTP,TestFP,TestFN,TestTN),nrow=2,ncol=2))
```

```{r}
CVLogisticFit <- glm(formula= Output ~ Area + Area^2 + Ellipticity..oblate. + Ellipticity..oblate.^2 + Ellipticity..prolate. + Ellipticity..prolate.^2 + Intensity.Max + Intensity.Mean + 
                   Intensity.Median + Intensity.Min + Intensity.StdDev + Intensity.Sum + Number.of.Vertices + Number.of.Vertices^2 + Sphericity + Sphericity^2
                     + Volume + Volume^2, 
                   data=as.data.frame(TrainData), 
                   family=binomial(link='logit'))
CVLogisticFit$coefficients
```
```{r}
TrainTP <- sum(TrainingOutputs & (CVLogisticFit$fitted.values>0.5))
TrainTN <- sum(!TrainingOutputs & !(CVLogisticFit$fitted.values>0.5))
TrainFP <- sum(!TrainingOutputs & (CVLogisticFit$fitted.values>0.5))
TrainFN <- sum(TrainingOutputs & !(CVLogisticFit$fitted.values>0.5))
Accuracy <- (TrainTP+TrainTN)/(TrainTP+TrainTN+TrainFP+ TrainFN)
Accuracy
```

```{r}
CVPredictions <- predict(CVLogisticFit,as.data.frame(cbind(TestingInputs,TestingOutputs)),type="response")
```

```{r}
TestTP <- sum(TestingOutputs & (CVPredictions>0.5))
TestTN <- sum(!TestingOutputs & !( CVPredictions >0.5))
TestFP <- sum(!TestingOutputs & (CVPredictions >0.5))
TestFN <- sum(TestingOutputs & !( CVPredictions >0.5))

Accuracy <- (TestTP+TestTN)/(TestTP+TestTN+TestFP+ TestFN)
Accuracy
```
```{r}
chisq.test(matrix(data=c(TestTP,TestFP,TestFN,TestTN),nrow=2,ncol=2))
```
